Global adjoint tomography -- Model GLAD-M25

### 2019-01-16 main.tex
add more figures

Figure~\ref{fig:global-average} shows the resulting radial averages of the isotropic shear and compressional wavespeeds for model~GLAD-M25
compared to 1D starting model~STW105~\citep{kustowski2008anisotropic} and PREM~\citep{PREM}.
The radial average of~GLAD-M25 remains very close to the radial starting model~STW105.
The main difference between these two models and~PREM
is the absence of the 220~km discontinuity and a lower~$V_p/V_s$ ratio in the top 200~km.
\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/1d_profile.pdf}
  \caption{1D radial shear and compressional wavespeed profiles for GLAD-M25, STW105, and PREM.
  The reference frequency for physical dispersion is~{\color{red} ??}~Hz.}
  \label{fig:global-average}
\end{figure}

>>>>

Figure~\ref{fig:global-average} shows the resulting radial averages of the isotropic shear and compressional wavespeeds for model~GLAD-M25
compared to 1D starting model~STW105~\citep{kustowski2008anisotropic} and PREM~\citep{PREM}.
The radial average of~GLAD-M25 remains very close to the radial starting model~STW105.
The main difference between these two models and~PREM
is the absence of the 220~km discontinuity and a lower~$V_p/V_s$ ratio in the top 200~km.

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/1d_profile.pdf}
  \caption{1D radial shear and compressional wavespeed profiles for GLAD-M25, STW105, and PREM.
  The reference frequency for physical dispersion is~{\color{red} ??}~Hz.}
  \label{fig:global-average}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/1d_profile_ra.pdf}
  \caption{1D radial-anisotropic shear and compressional wavespeed profiles for GLAD-M25 and STW105. The reference frequency for physical dispersion is~{\color{red} ??}~Hz.}
  \label{fig:global-ra-average}
\end{figure}

\section{Window distributions}

Fig.\ref{fig:window_density} shows the window density map on the
vertical component for 17-40 sec period band. In this category,
we picked in total of 4,363,719 time windows. The color denotes the
density of windows. X axis is the time and y axis is the epicenter
distance. Windows are discretized into 1 degree in epicenter distance
domain and 1 second in time domain.

The max density value of windows is 9,931, located at 134-135 epicenter
distance bin and 1375-1376 time bin.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
  \caption{The window density map.}
  \label{fig:window_density}
\end{figure}
